Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-27 appendix.tex
Appendix Figure 5 and updated notebook

>>>>

\begin{enumerate}
    \item Get a log file including regular polling of backfill availability from one or more PanDA Brokers on titan.
    \item Wrangle the ascii file with the find/replace regular expressions listed at: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/figure_5/titan_backfill_availability.ipynb}, cell \#1.
    \item Load the Jupyter workbook from a python virtual environment with the module Jupyter installed and all the modules listed at: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/blob/master/data/figure_5/titan_backfill_availability.ipynb}, cell \#2.
    \item Execute each cell of the Jupyter notebook to replicate Figure 5.
\end{enumerate}
